\documentclass{article}
\usepackage{amsmath}
\usepackage{tikz-cd}
\usepackage{enumerate}

\begin{document}
\subsection*{Goals}
\begin{itemize}
    \item Make a MUD
\end{itemize}

\begin{equation*} \label{g1}
\begin{tikzcd}
    & \text{Info} \arrow[dr] & \text{Material} \arrow[d]
    & \text{Enchantments} \arrow[dl] \\
    && \text{Item} \ar[dll] \ar[dl] \ar[d] \ar[dr] \ar[drr] \\
    \text{Weapon} & \text{Clothing} & \text{Consumable} & \text{Landmark} & \text{Container}
    \end{tikzcd}
\end{equation*}

\subsection*{Descriptions}
\textbf{Item:} Has data members durability, weight, weight-distribution, flexibility, 

\subsubsection*{Forward Declared Dependencies}
\begin{enumerate}
    \item \textbf{Info:} Contains external description of item. This
    includes how it looks, size, and volume-type. Size and volume type
    factor into what said item can fit into and weight distribution.  
    Also contains unique ID and name.

    \item \textbf{Material:} Contains information regarding the
    material of the item. This factors primarily into things like
    durability, weight, density, and flexibility. 

    \item \textbf{Enhancements:} Contains information regarding how
    this item affects the statistics of the one who posesses it or the
    one it's used on.
\end{enumerate}

\subsubsection*{Child Classes (Dependants in which `Item' is Included)}
\begin{enumerate}
    \item \textbf{Weapon:} Has data members damage-type.

    \item \textbf{Clothing:} Has data members defense, 
        wearable-locations.

\end{enumerate}

\subsection*{Possible Commands} \subsubsection*{Weaponry} jab, light
swing, medium swing, heavy swing, parry, guard, special

\subsubsection*{Clothing} wear

\bigskip
\bigskip
\hline 

\subsection*{Ideas}
\begin{itemize}
    \item Combat like Vindictus/PSO. It needs to be \textit{that} good.
        \begin{itemize}
            \item Step forward when swing (using attacks as movement)
            \item Fast-paced
        \end{itemize}
    \item Environment/tiles/depth like MineCraft
    \item Graphics like Final Fantasy Tactics (maybe taller)
    \item Card Game like FF8 or FF9
    \item A primary tower-dungeon like Sword Art Online (but with a 
        whole world built around it; it doesn't consist of just the
        tower-dungeon).
    \item Play some .Hack and see how that combat is.

\end{itemize}
\end{document}
