\documentclass{article}
\usepackage{amsmath}
\usepackage{tikz-cd}
\usepackage{enumerate}

\begin{document}
\subsection*{Goals}
\begin{itemize}
    \item Make a MUD
\end{itemize}

\begin{equation*} \label{g1}
\begin{tikzcd}
    & \text{Info} \arrow[dr] & \text{Material} \arrow[d]
    & \text{Enchantments} \arrow[dl] \\
    && \text{Item} \ar[dll] \ar[dl] \ar[d] \ar[dr] \ar[drr] \\
    \text{Weapon} & \text{Clothing} & \text{Consumable} & \text{Landmark} & \text{Container}
    \end{tikzcd}
\end{equation*}

\subsection*{Descriptions}
\textbf{Item:} Has data members durability, weight, weight-distribution, flexibility, 

\subsubsection*{Item Ideas}
\begin{enumerate}
    \item \textbf{Info:} Contains external description of item. This
    includes how it looks, size, and volume-type. Size and volume type
    factor into what said item can fit into and weight distribution.  
    Also contains unique ID and name.

    \item \textbf{Material:} Contains information regarding the
    material of the item. This factors primarily into things like
    durability, weight, density, and flexibility. 

    \item \textbf{Enhancements:} Contains information regarding how
    this item affects the statistics of the one who posesses it or the
    one it's used on.
\end{enumerate}

\subsubsection*{Potential Composition modules for item }
\begin{enumerate}
    \item \textbf{Weapon:} Has data members damage-type.

    \item \textbf{Clothing:} Has data members defense, 
        wearable-locations.

\end{enumerate}

\subsection*{Possible Commands}

Commands are [noun] [verb] [location]. There must always be a verb. 
Sometimes that verb requires a noun (i.e. - get item). 
Optionally, one may specify a location (i.e. - get item from 
container). Words like "from" etc. will just be ignored. Don't spend 
too much time on this; it's not really relevant.

\bigskip
\bigskip

\hline 

\subsection*{Ideas}
\begin{itemize}
    \item Combat like Vindictus/PSO. It needs to be \textit{that} good.
        \begin{itemize}
            \item Step forward when swing (using attacks as movement)
            \item Fast-paced
            \item Somewhat long-ranged melee weapons
            \item Every attack is "premeditated"
        \end{itemize}
    \item Environment/tiles/depth like MineCraft
    \item Graphics like Final Fantasy Tactics (maybe taller; maybe more like FF9)
    \item Card Game like FF8 or FF9
    \item A primary tower-dungeon like Sword Art Online (but with a 
        whole world built around it; it doesn't consist of just the
        tower-dungeon). The dungeon is randomly generated. The world
        is not.
    \item Circular world? Dungeon in the center with many floors.
        Each floor randomly generates.
    \item No one can see each other's level or equipment
        explicitely (only how it looks, how strong a person is, etc.)
        You can see HP, though.
    \item NEURO: Concentrate for special attack. Black and white.  
        Soothing voice: "Breath..." Everything around silences.
    \item Anonymous skills (you don't know why you get them, they 
        just appear) and skill requirements. The skill "tree"
        branches from that single skill. Think: "Dual-wielding" in 
        SwordArt.
    \item No map/radar/etc. Maybe have a paper item on which players
        can draw a map of the world. They won't have "You are Here"
        on them, though. It's just a regular map. 
    \item No "whispering" (what the fuck is that shit). Sent mail
        messages will take some time to get to their respective party.
        Chat will be done when two characters are face to face (or
        via some magic).
    \item Long-distance magics that target some player; maybe
        something like a gateway that will allow communication 
        between two parties; a black-magic caster must use this,
        for example
    \item Long respawn timer. Soul leaves "soulfire" item upon death. 
        People can pick it up, respawn it, etc. Really decentivize 
        death.


\end{itemize}

\end{document}
